\begin{center}
  \large\textbf{ABSTRACT}
\end{center}

\addcontentsline{toc}{chapter}{ABSTRACT}

\vspace{2ex}

\begingroup
% Menghilangkan padding
\setlength{\tabcolsep}{0pt}

\noindent
\begin{tabularx}{\textwidth}{l >{\centering}m{3em} X}
  % Ubah kalimat berikut dengan nama mahasiswa
  \emph{Name}     & : & \name{}         \\

  % Ubah kalimat berikut dengan judul tugas akhir dalam Bahasa Inggris
  \emph{Title}    & : & \engtatitle{}   \\

  % Ubah kalimat-kalimat berikut dengan nama-nama dosen pembimbing
  \emph{Advisors} & : & 1. \advisor{}   \\
                  &   & 2. \coadvisor{} \\
\end{tabularx}
\endgroup

% Ubah paragraf berikut dengan abstrak dari tugas akhir dalam Bahasa Inggris
\emph{The Metaverse is a set of virtual spaces, where one can create and browse with other internet users who are not in the same physical space
  with that person. The application often uses blockchain as a solution
  decentralized. The Metaverse itself certainly requires an audio output, which is realized
  by Unreal Engine 5 with its metasound feature.
  Merging the two can be achieved by using smart contracts. Then in
  This research will create a system that can make this happen with the help of Ethereum
  Smart Contract, NFT to store metadata, and IPFS web3.storage to store
  audio source files for metasound.
  With the existence of a decentralized system, it is also hoped that interoperability will be realized.
  ability to make this metaverse usable and communicate with other blockchain platforms.
  As long as the Blockchain Network supports the ERC-721 Protocol, each network can still communicate with 
  each other. In the testing, we conducted tests on calling smart contract methods, the complexity of methods 
  with gas usage, and integration with Unreal Engine 5. This system utilizes real-time audio data transfer in 
  Unreal Engine 5, and also uses several supporting plugins such as Runtime Audio Importer.}

% Ubah kata-kata berikut dengan kata kunci dari tugas akhir dalam Bahasa Inggris
\emph{Keywords}: \emph{Rocket}, \emph{Anti-gravity}, \emph{Energy}, \emph{Space}.
